---
title: "find_betfair_worldcup2018_markets"
author: "Nima Hamedani-Raja"
date: "29 May 2018"
output: 
  html_document: 
    keep_md: yes
---

## About 

A piece of (exploratory) code to find the IDs of betfair World Cup markets. I'll use these IDs to regularly sample the market.  
I am using [abettor](https://github.com/phillc73/abettor) here. Many thanks to [phillc73](https://github.com/phillc73).  
also see [betfair developer program](http://docs.developer.betfair.com/docs/display/1smk3cen4v3lu3yomq5qye0ni/Getting+Started).  

## INIT

Install and load abettor.

```{r abettor}
# devtools::install_github("phillc73/abettor")
library("abettor")
```

load other libraries.

```{r libraries}
library(knitr)
```


Load username, password, and application key. *as if I am uploading them to a public repo!*

```{r load_upa}
nima <- read.csv("my_login_data.csv")

logoutBF(suppress = TRUE, sslVerify = TRUE)

loginBF(username = nima$username, 
        password = nima$password, 
        applicationKey = as.character(nima$applicationKey))
```

## Odds for a given market  

Find eventtype.id for football:  

```{r eventtype.id}
eventtypes <- listEventTypes()

eventtypes

football_eventtypeid <- subset(eventtypes$eventType, name == "Soccer")$id

football_eventtypeid
```

List all football competitions. Make sure toDate is set to a date *after* the final match, default value is tomorrow.    

```{r listCompetitions}
football_competitions <- 
    listCompetitions(eventTypeIds = football_eventtypeid, 
                     toDate = "2019-05-30T12:00:00Z")

head(football_competitions)

worldcup_competitionid <- 
    subset(football_competitions$competition, 
           name == "2018 FIFA World Cup")$id

worldcup_competitionid
```

List MarketTypes:  

```{r markettypes}
all_MarketTypes <- 
    listMarketTypes(eventTypeIds = football_eventtypeid, 
                    competitionIds = worldcup_competitionid, 
                    toDate = "2019-05-30T12:00:00Z")
all_MarketTypes
```

For now, I am only interested in WINNER. 

Get MarketCatalogue:  

```{r marketcatalogue}
Winner_MarketCatalogue <- 
    listMarketCatalogue(eventTypeIds = football_eventtypeid, 
                        competitionIds = worldcup_competitionid, 
                        toDate = "2019-05-30T12:00:00Z", 
                        marketTypeCodes = "WINNER")

Winner_MarketCatalogue

Winner_marketId <- 
    Winner_MarketCatalogue$marketId

Winner_marketId
```

Get the odds: 

```{r marketbook}
Winner_MarketBook <- listMarketBook(marketIds = Winner_marketId, priceData = "EX_ALL_OFFERS")
Winner_MarketBook$runners 

```

## Find all submarkets of a market


```{r submakets}
all_events <- listEvents(eventTypeIds = football_eventtypeid, 
                         competitionIds = worldcup_competitionid, 
                         toDate = "2019-05-30T12:00:00Z")

OpeningMatch_id <- subset(all_events$event, name == "Russia v Saudi Arabia")$id

OpeningMatch_Catalogue <- 
    listMarketCatalogue(eventTypeIds = football_eventtypeid, 
                        competitionIds = worldcup_competitionid, 
                        toDate = "2019-05-30T12:00:00Z", 
                        eventIds = OpeningMatch_id,
                        marketTypeCodes = all_MarketTypes$marketType)                    

OpeningMatch_Catalogue
```

```{r logout}
logoutBF(suppress = TRUE, sslVerify = TRUE)
```


